Preprocessing

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

Make a tibble containing only the final coding for journals.

```{r}
d_journals_final <- d_journals %>%
  filter(coder_id == "FINAL (TEH)") %>% # select only the final coding
  select(-coder_id, -timestamps) # drop the coder_id and timestamps columns
```

@@

```{r}
d_journals_final <- d_journals_final %>%
  pivot_longer( # pivot to long format
    cols = c(-journal,-journal_empirical,-sample_id,-anyPPC,-general_note),
    names_to = c("PPC_type", ".value"), 
    names_sep = "_ppc_"
  )
```

@@

```{r}
d_journals_final <- d_journals_final %>% 
  mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
         length_harmonized = str_remove(length_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         length_harmonized = case_when(
           length_harmonized == "1,000 words" ~ "1000",
           length_harmonized == "1,500 words (one figure and/or one table allowed within word count)" ~ "1500",
           length_harmonized == "1000 words" ~ "1000",
           length_harmonized == "16 pages" ~ as.character(16*pageToWord),
           length_harmonized == "2000 words" ~ "2000",
           length_harmonized == "265 lines of text including references" ~ as.character(265*linesToWord),
           length_harmonized == "3500 words (title page and references included)" ~ "3500",
           length_harmonized == "400 words" ~ "400",
           length_harmonized == "5 pages, including abstract, references, tables, and figures." ~ as.character(5*pageToWord),
           length_harmonized == "500 words" ~ "500",
           length_harmonized == "600-800 words" ~ "800",
           length_harmonized == "750 words" ~ "750",
           length_harmonized == "Approx. 1,000 words" ~ "1000",
           length_harmonized == "approximately 1,000 words" ~ "1000",
           length_harmonized == "as concise as possible, and ideally not exceed 1,200 words" ~ "1200",
           length_harmonized == "at maximum half the length of the target article." ~ "Qualitative",
           length_harmonized == "Maximum length: 1100 words." ~ "1100",
           length_harmonized == "short" ~ "Qualitative",
           length_harmonized == "up to 2,000 words counting 500 words per table and figure" ~ "2000",
           TRUE ~ length_harmonized
         )) 
```

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(time_harmonized = str_remove_all(time, pattern = '"'), #  remove any quotation marks
         time_harmonized = str_remove(time_harmonized, pattern = fixed("YES (provide detail of time limits below), ")),# remove data entry question text
         time_harmonized = case_when(
           time_harmonized == "3 months" ~ as.character(3*monthToWeek),
           time_harmonized == "6 months" ~ as.character(6*monthToWeek),
           time_harmonized == "9 months" ~ as.character(9*monthToWeek),
           time_harmonized == "Draft proposed comments will be due on a tight time- line (i.e., 2– 4 weeks after solicitation), to be determined by the Editor." ~ "4",
           time_harmonized == "he Commentary mechanism is most effective when used to address a contemporary publication" ~ "Qualitative",
           time_harmonized == "Matters Arising articles are interesting and timely scientific or academic comments" ~ "Qualitative",
           time_harmonized == "recent" ~ "Qualitative",
           time_harmonized == "recently published" ~ "Qualitative",
           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), recently published" ~ "Qualitative",
           time_harmonized == "YES (copy and paste the limits in the 'other' section below), 1-year (except for a test of replication)" ~ as.character(1*yearToWeek),
           TRUE ~ time_harmonized
         )) 
```

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(ref_harmonized = str_remove_all(ref, pattern = '"'), #  remove any quotation marks
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         ref_harmonized = case_when(
           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
           ref_harmonized == "contributions may have up to 15 references" ~ "15",
           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
           ref_harmonized == "No more than 5 references" ~ "5",
           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
           TRUE ~ ref_harmonized
         )) 
```

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(review_harmonized = case_when(
           review == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
           review == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
           review == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response. The comments and formal response may then be sent to independent referees.'" ~ "YES",
           TRUE ~ review
         )) 
```

@@

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>%
  mutate(name_harmonized = case_when(
    name %in% commentaries ~ "Commentary",
    name %in% letters ~ "Letters",
    name %in% other ~ "Other"
  ))
```

@@

@@

>>>>

Retain only the final coding for journals.

```{r}
d_journals <- d_journals %>%
  filter(coder_id == "FINAL (TEH)") %>% # select only the final coding
  select(-coder_id, -timestamps) # drop the coder_id and timestamps columns
```

@@

```{r}
d_journals <- d_journals %>%
  pivot_longer( # pivot to long format
    cols = c(-journal,-journal_empirical,-sample_id,-anyPPC,-general_note),
    names_to = c("PPC_type", ".value"), 
    names_sep = "_ppc_"
  )
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(length_harmonized = str_remove_all(length, pattern = '"'), #  remove any quotation marks
         length_harmonized = str_remove(length_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         length_harmonized = case_when(
           length_harmonized == "1,000 words" ~ "1000",
           length_harmonized == "1,500 words (one figure and/or one table allowed within word count)" ~ "1500",
           length_harmonized == "1000 words" ~ "1000",
           length_harmonized == "16 pages" ~ as.character(16*pageToWord),
           length_harmonized == "2000 words" ~ "2000",
           length_harmonized == "265 lines of text including references" ~ as.character(265*linesToWord),
           length_harmonized == "3500 words (title page and references included)" ~ "3500",
           length_harmonized == "400 words" ~ "400",
           length_harmonized == "5 pages, including abstract, references, tables, and figures." ~ as.character(5*pageToWord),
           length_harmonized == "500 words" ~ "500",
           length_harmonized == "600-800 words" ~ "800",
           length_harmonized == "750 words" ~ "750",
           length_harmonized == "Approx. 1,000 words" ~ "1000",
           length_harmonized == "approximately 1,000 words" ~ "1000",
           length_harmonized == "as concise as possible, and ideally not exceed 1,200 words" ~ "1200",
           length_harmonized == "at maximum half the length of the target article." ~ "Qualitative",
           length_harmonized == "Maximum length: 1100 words." ~ "1100",
           length_harmonized == "short" ~ "Qualitative",
           length_harmonized == "up to 2,000 words counting 500 words per table and figure" ~ "2000",
           TRUE ~ length_harmonized
         )) 
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(time_harmonized = str_remove_all(time, pattern = '"'), #  remove any quotation marks
         time_harmonized = str_remove(time_harmonized, pattern = fixed("YES (provide detail of time limits below), ")),# remove data entry question text
         time_harmonized = case_when(
           time_harmonized == "3 months" ~ as.character(3*monthToWeek),
           time_harmonized == "6 months" ~ as.character(6*monthToWeek),
           time_harmonized == "9 months" ~ as.character(9*monthToWeek),
           time_harmonized == "Draft proposed comments will be due on a tight time- line (i.e., 2– 4 weeks after solicitation), to be determined by the Editor." ~ "4",
           time_harmonized == "he Commentary mechanism is most effective when used to address a contemporary publication" ~ "Qualitative",
           time_harmonized == "Matters Arising articles are interesting and timely scientific or academic comments" ~ "Qualitative",
           time_harmonized == "recent" ~ "Qualitative",
           time_harmonized == "recently published" ~ "Qualitative",
           time_harmonized == "UNCLEAR (provide detail in the 'other' section below), recently published" ~ "Qualitative",
           time_harmonized == "YES (copy and paste the limits in the 'other' section below), 1-year (except for a test of replication)" ~ as.character(1*yearToWeek),
           TRUE ~ time_harmonized
         )) 
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(ref_harmonized = str_remove_all(ref, pattern = '"'), #  remove any quotation marks
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         ref_harmonized = case_when(
           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
           ref_harmonized == "contributions may have up to 15 references" ~ "15",
           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
           ref_harmonized == "No more than 5 references" ~ "5",
           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
           TRUE ~ ref_harmonized
         )) 
```

@@

```{r}
d_journals <- d_journals %>% 
  mutate(review_harmonized = case_when(
           review == "NO, This correspondence is published at the discretion of the Editor-in-Chief and the Associate Editors" ~ "NO",
           review == "NOT STATED, The guidelines discuss peer review, but it appears that this discussion isn't relevant to commentary articles." ~ "NOT STATED",
           review == "UNCLEAR (provide detail in the 'other' section below), It 'may' be sent for independent review: 'Matters Arising submissions that meet the journal’s criteria are sent to the authors of the original paper for a formal response. The comments and formal response may then be sent to independent referees.'" ~ "YES",
           TRUE ~ review
         )) 
```

@@

```{r}
d_journals <- d_journals %>%
  mutate(name_harmonized = case_when(
    name %in% commentaries ~ "Commentary",
    name %in% letters ~ "Letters",
    name %in% other ~ "Other"
  ))
```
# Reclassify and reformat

Reclassify some values like "Yes" and "No" into logicals, format some columns, and select only columns we need for data analysis.

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = fct_recode(journal_empirical, T = "Yes", F = "No"),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized)
```

```{r}
d_articles <- d_articles %>%
  mutate(sample_id = factor(sample_id),
         article_id = factor(article_id),
         exclude = factor(exclusion_final),
         exclude_reason = factor(exclusion_reason_final),
         ppc_linked = fct_recode(ppc_linked_final, T = "NO", F = "YES")) %>%
  select(sample_id, article_id, exclude, exclude_reason, ppc_linked)
```

@@

We'll run some final tests in this section to make sure we have what we expect in each column.

@@

# Export files to processed data folder

The data is now ready for analysis! Let's export it to the 'processed' data folder.

```{r}
write_csv(d_articles, here('data','processed','d_articles.csv'))
write_csv(d_journals, here('data','processed','d_journals.csv'))
```
